### 2009-07-15 paper.tex
Production edits

% Please keep the abstract between 250 and 300 words
\newpage
\section*{Abstract}
% The existence of an all-RNA primordial ribosome was proposed by
% Francis Crick in 1968.  Recently, a domain-level model for the
% original ribosome was proposed by Smith et al.  Given the abundance of
% ribosomal RNA sequence data and the many successful reconstructions of
% ancestral proteins, the reconstruction and synthesis of ancestral
% ribosomes (and other RNAs) is a feasible goal for paleogenetics.  This
% will require new bioinformatics tools and methods, in particular a
% robust theoretical framework for reconstructing histories of
% substitutions, indels and changes in RNA structure.

@@

In our tests, incorporation of basepair structure was the most
important factor for accurate inference of alignment; appropriate use
of posterior-decoding was the next most important factor; and fine
details of the model were least important.  Posterior-decoding
heuristics can be substantially faster than exact phylogenetic
inference, so this motivates the use of sum-over-pairs (and
approximate sum-over-pairs) heuristics where possible.  For more exact
probabilistic inference, we discuss the use of transducer composition
for ML (or MCMC) inference on phylogenies, including possible ways to
make the core operations tractable.

>>>>

% Please keep the abstract between 250 and 300 words
\newpage
\section*{Abstract}
% The existence of an all-RNA primordial ribosome was proposed by
% Francis Crick in 1968.  Recently, a domain-level model for the
% original ribosome was proposed by Smith et al.  Given the abundance of
% ribosomal RNA sequence data and the many successful reconstructions of
% ancestral proteins,

The reconstruction and synthesis of ancestral RNAs is a feasible goal for paleogenetics.
This will require new bioinformatics methods, including a
robust statistical framework for reconstructing histories of
substitutions, indels and structural changes.

@@

In our tests, incorporation of basepair structure was the most
important factor for accurate alignment inference; appropriate use
of posterior-decoding was next; and fine
details of the model were least important.  Posterior-decoding
heuristics can be substantially faster than exact phylogenetic
inference, so this motivates the use of sum-over-pairs heuristics where possible
(and approximate sum-over-pairs).  For more exact
probabilistic inference, we discuss the use of transducer composition
for ML (or MCMC) inference on phylogenies, including possible ways to
make the core operations tractable.
